pollen_countR

### 2024-03-30 script/SpecimensSequencedTable.Rmd
ideally simplyfing repo for code submission

---
output: pdf_document
classoption: landscape
geometry: "left=1cm,right=1cm,top=1cm,bottom=1cm"
header-includes:
  - \usepackage{titlesec}
  - \pagenumbering{gobble}
  - \titlespacing{\title}{0pt}{\parskip}{-\parskip}
---

\vspace{-25truemm}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

>>>>

---
output: pdf_document
classoption: landscape
geometry: "left=1cm,right=1cm,top=1cm,bottom=1cm"
header-includes:
  - \usepackage{titlesec}
  - \usepackage{caption}
  - \pagenumbering{gobble}
  - \titlespacing{\title}{0pt}{\parskip}{-\parskip}
---

\captionsetup[table]{labelformat=empty}
\vspace{-25truemm}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

### 2024-03-30 script/SupplementaryInformation.Rmd
ideally simplyfing repo for code submission

---
title: "Supplemental Information"
author: "steppe"
output:
  pdf_document: default
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r Create Table 1}

variable <- c(
  rep('Climate', times = 4),
  rep('Elevation', times = 4), 
  rep('Land Uses / Land Covers', times = 4), 
  rep('Vegetation Cover', times = 1), 
  rep('Soils & Geomorphology', times = 4)
)

@@

```{r}
knitr::kable(
  df, 
  caption = info, 
  col.names = c('Variable', 'Data Source', 'Geographic Extent'),
  booktabs = TRUE, 
  format  = "latex",
  longtable = FALSE
  ) |> 
  kableExtra::row_spec(0,bold=TRUE) |>
  kableExtra::collapse_rows(1) |>
  kableExtra::kable_styling(latex_options="scale_down") |>
  kableExtra::add_footnote('CONUS; CONtinental United States')

@@

```{r Site Maps, echo = F}
knitr::include_graphics('../graphics/plots/siteMaps.png')
```

@@

```{r Voucher Reference Specimen table 1, echo = F}
knitr::include_graphics('../graphics/tables/specimen_table_v2.png')
```

Figure 2 - Pollen Key

@@

Table 6 - Binary reclassification process

>>>>

---
title: "Supplemental Information"
author: "steppe"
output:
  pdf_document: default
---
```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r Create Table 1}
variable <- c(
  rep('Climate', times = 4),
  rep('Elevation', times = 4), 
  rep('Land Uses / Land Covers', times = 4), 
  rep('Vegetation Cover', times = 1), 
  rep('Soils & Geomorphology', times = 4)
)

@@

```{r}
knitr::kable(
  df, 
  caption = info, 
  col.names = c('Variable', 'Data Source', 'Geographic Extent'),
  booktabs = TRUE, 
  format  = "latex",
  longtable = FALSE
  ) |> 
  kableExtra::row_spec(0,bold=TRUE) |>
  kableExtra::collapse_rows(1) |>
  kableExtra::kable_styling(latex_options="scale_down") |>
  kableExtra::add_footnote('CONUS; CONtinental United States') |>
  kableExtra::kable_styling(latex_options = "HOLD_position")

@@

```{r Site Maps, echo = F, out.width="90%"}
knitr::include_graphics('../graphics/plots/siteMaps.png')
```

@@

```{r Voucher Reference Specimen table 1, echo = F, out.height="90%"}
knitr::include_graphics('../graphics/tables/specimen_table_v2.png')
```

\newpage
Figure 2 - Pollen Key

@@

Table 6 - Binary Reclassification Process

### 2024-03-30 script/pollen_countr3.Rmd
ideally simplyfing repo for code submission

---
title: "pollen_countR"
author: "Reed & Emily"
date: "4/9/2021"
output: 
  pdf_document:
      fig_caption: true
      number_sections: true
      includes:
        in_header: float_free.tex
---

>>>>

---
title: "pollen_countR"
author: "steppe & EJW"
date: "4/9/2021"
output: 
  pdf_document:
      fig_caption: true
      number_sections: true
      includes:
        in_header: float_free.tex
---
